### 2020-01-14 report/02-methods.Rmd
Pielou et betadiv en biomass instead of individual number

@@

>>>>

- A metaweb was built:
  - less computational intensive

When you do a metaweb, you kind of consider that you have one type of community
in terms of species interaction:
  - Trophic lvl is defined at the metaweb lvl, different from the realized
    metaweb

@@

#### Description of horizontal Community structure

- Pielou computed on biomass:
  - pielou does not depend on total biomass (same value if computed on raw
    biomass or relattive biomass)

- Binary betadiversity computed on biomass:
  - betadiversity-bin is the same if computed on biomass or individual number 
  - betadiversity-bin computed on biomass is correlated at .72 with the one
    computed with individual numbers.

- Species richness
